MINOS Handover Plots

### 2023-05-17 minos/validation/handovers.Rmd
Embarassing fix here. Forgot to remove missing values from the raw data in handover plots (assumed that this had been done during complete_case but that was only for some variables). This has changed the shape of the SF12 MCS and PCS plots, and shows some problematic behaviour that needs to be monitored. I believe these will be vastly improved with the rate of change model work that is ongoing, but remains to be seen

@@

```{r}
raw.neighbour <- raw.dat %>% 
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

```{r}
raw.loneliness <- raw.dat %>% 
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

>>>>

print(sum(sf12.m$SF_12_MCS < 0))

@@

```{r}
raw.neighbour <- raw.dat %>% 
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  filter(neighbourhood_safety > 0) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  filter(neighbourhood_safety > 0) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

```{r}
raw.loneliness <- raw.dat %>% 
  dplyr::select(pidp, time, loneliness) %>%
  filter(loneliness > 0) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  filter(loneliness > 0) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(phealth >= 0) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')
